---
title: "p8105_hw1_jr4550"
output: github_document
date: Sept 20, 2025
---

I'm an R Markdown document! 

## Problem 1 

### loading moderndive and early_january_weather dataset 

```{r setup}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```


### early_january_weather Description
           
Number of rows = 358           
```{r}
nrow(early_january_weather)
```

Number of columns = 15  
```{r}
ncol(early_january_weather)
```

The mean of the Temperature is 39.58212
```{r}
mean(early_january_weather$temp)
```

Variable names and values
```{r}
head(
early_january_weather)
```


```{r}
write.csv(early_january_weather, "early_january_weather.csv", row.names = FALSE)

```


### Scatterplot 

In the scatterplot, from January 1-23, 2013 we see that around January 10th humidity starts to increase. Average temperature during this time was 39.58 fahrenheit. 
```{r yx_scatter}
ggplot(early_january_weather, aes(x = time_hour, y = temp, colour = humid)) + 
    geom_point()
```
```{r}
ggsave("temp_vs_time.png", width = 8, height = 5)
```

## Problem 2
### Create data frame 

```{r}
library(tidyverse)
```

```{r}
example_df = tibble(
  vec_numeric = rnorm(10),
  vec_char = c("My", "name", "is", "Jeff", "and", "I", "am", "taking", "data", "science"),
  vec_logical = c(TRUE, TRUE, TRUE, FALSE,TRUE, TRUE, TRUE, FALSE,FALSE,FALSE),
  vec_factor = factor(c("male", "male", "trans", "female","trans", "male", "female", "female","female", "female"))
)
```


 
```{r}
mean(pull(example_df, vec_numeric))
mean(pull(example_df, vec_char))
mean(pull(example_df, vec_logical))
mean(pull(example_df, vec_factor))

```
### Converting Varibles to numeric

```{r}
as.numeric(pull(example_df, vec_char))
as.numeric(pull(example_df, vec_logical))
as.numeric(pull(example_df, vec_factor))
```

```{r}
mean(as.numeric(pull(example_df, vec_char)))
mean(as.numeric(pull(example_df, vec_logical)))
mean(as.numeric(pull(example_df, vec_factor)))
```

